SoK: Defending Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-15 docs/questioning.tex
removed the text about average overhead
csrf

We provide a step-by-step exploitation model to understand the process
of carrying out code injection attacks against web
applications. Figure~\ref{fig:attacks} presents the required steps for
different classes of injection attacks. Links between steps are
labeled with the different attacks that use that path, while the
numbers next to attack labels denote the sequence of steps for a
particular attack. Most steps are common in all attacks. This is
because they are based on similar attack vectors as we mentioned in
the previous section. Large `X' marks on transitions indicate the
points where defenses detect or prevent attacks.

An attacker can initiate an injection attack through two different main routes.
One way is to use the browser of a victim as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could craft a malicious script into a {\sc
  url} and then trick a user to click on it through social
engineering, e.g., by sending a phishing email (transition {\sc p-xss} 1.1, {\sc
  n-xss} 1.1). Alternatively, the attacker may be able
to inject directly the malicious code on the server through an {\sc http} request
({\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1, {\sc csrf} 1). This would happen
in a web application that accepts and processes user input
without appropriate validation. An attacker could upload data
containing a specially crafted script
to steal the cookies of the visiting users ({\sc p-xss} 1, {\sc n-xss} 1),
an {\tt img} tag including a malicious {\sc http} request ({\sc csrf}),
or embed malicious
{\sc sql} code to retrieve the password entries from a database ({\sc dsl} 1).
%Recall the examples we provided in Section~\ref{sec:attacks}.
Note that {\sc xss} attacks can start from both routes.

Once the injected code reaches the vulnerable application, it becomes
a part of a value represented by a program variable. The target of the
attack determines the route from now on. In an {\sc sql} injection
attack the injected code becomes part of a query that
finally reaches the database where it is executed.

{\sc xss} attacks fall into two categories, {\it non-persistent} and
{\it persistent}. Non-persistent {\sc xss} attacks take place when the
data provided by a user is processed on-the-fly
by server-side application logic and end up without proper sanitization
into a dynamically generated response ({\sc p-xss} 7, {\sc n-xss} 2)
that is eventually rendered by the user's browser.
Thus, in a non-persistent {\sc xss} attack, the injected code
is not saved on the server and immediately becomes part of the
content that is sent back to a web user.
In persistent {\sc xss} attacks, on the other hand,
malicious code is permanently stored on the server ({\sc p-xss} 5).
The injected code residing at server-side then re-enters the
application's execution flow and becomes part of the content that is
actually sent back to the user as part of a future response.

A common {\sc csrf} attack could involve just a
{\sc url} containing a malicious {\sc http} request
which in turn must be clicked by the user
via social engineering again ({\sc csrf} 1).
Note, that this case does not involve code injection
and it never reaches the server that is vulnerable
to code injection (Server 1).
The {\sc i-csrf} attack involves an attacker
that manages to inject {\sc html} code that contains
a hidden request in the way we described in
Section~\ref{sec:attacks}. This code will be stored
in the database ({\sc i-csrf} 5)
and then it will re-enter the application if
a user visits a page ({\sc i-csrf} 6). When the
content reaches the browser the functionality
dictated by the malicious request will be performed.

>>>>

We provide a step-by-step exploitation model to aid in understanding the process
of carrying out code injection attacks against web
applications. Figure~\ref{fig:attacks} illustrates the required steps for
different classes of injection attacks,
such as SQL injection, XSS, and CSRF. Links between steps are
labeled with the different attacks that use that path, while the
numbers next to attack labels denote the sequence of steps for a
particular attack. Most steps are common in all attacks, as different attack
types follow similar exploitation paths, as mentioned in
the previous section. Large `X' marks on transitions correspond to the
points where the defenses we consider in this work detect or prevent attacks.

An attacker can initiate an injection attack through two main routes.
One way is to use the browser of a victim as an attack
vehicle, through which the code will be injected in the application.
For example, the attacker could embed a malicious script into a {\sc
  url} and then trick a user to click on it through social
engineering, e.g., by sending a phishing email (transition {\sc p-xss} 1.1, {\sc
  n-xss} 1.1, {\sc csrf} 1). Alternatively, the attacker may be able
to inject directly the malicious code on the server through an {\sc http} request
({\sc dsl} 1, {\sc p-xss} 1, {\sc n-xss} 1, {\sc i-csrf} 1). This would happen
in a web application that accepts and processes user input
without appropriate validation. An attacker could upload data
containing a specially crafted script
to steal the cookies of the visiting users ({\sc p-xss} 1, {\sc n-xss} 1),
an {\tt img} tag including a malicious {\sc http} request ({\sc csrf 1}, {\sc
i-csrf 1}),
or embed malicious
{\sc sql} code to retrieve private data from a database ({\sc dsl} 1).
%Recall the examples we provided in Section~\ref{sec:attacks}.
Note that {\sc xss} and {\sc csrf} attacks can start from both routes.

Once the injected code reaches the vulnerable application, it becomes
a part of a value represented by a program variable. The target of the
attack determines the route from that point and on. In an {\sc sql} injection
attack, the injected code becomes part of a query that
eventually reaches the database where it is executed.

Cross-site scripting attacks fall into two categories, {\it non-persistent}
(also known as \emph{reflected}) {\sc xss}
and {\it persistent} (also known as \emph{stored}) {\sc XSS}.
Non-persistent {\sc xss} attacks take place when the
data provided by a user is processed on-the-fly
by server-side application logic and ends up without proper sanitization
into a dynamically generated response ({\sc p-xss} 7, {\sc n-xss} 2)
that is eventually rendered by the user's browser.
Thus, in a non-persistent {\sc xss} attack, the injected code
is not saved on the server, but immediately becomes part of the
content that is sent back to a user.
In persistent {\sc xss} attacks, on the other hand,
malicious code is permanently stored on the server ({\sc p-xss} 5).
The injected code residing at server side then re-enters the
application's execution flow and becomes part of the content that is
eventually sent to the user as part of a future response.

Cross-site request forgery attacks typically involve just a
URL or page that contains a malicious request towards
a site vulnerable to {\sc csrf}.
An attacker can entice a victim to click on the URL or visit the page
through social engineering ({\sc csrf} 1), which will the result in a malicious
request towards the vulnerable site ({\sc csrf} 2}).
Note that this scenario does not involve the injection of any code through the
exploitation of some server-side vulnerability (as is the case with Server 1).
On the other hand, {\sc csrf} is also possible through injection
({\sc i-csrf}). In this attack, an attacker
manages to inject {\sc html} code that contains
a malicious {\sc csrf} request in the way we described in
Section~\ref{sec:attacks}.
This code will be stored
in the database ({\sc i-csrf} 5)
and then it will re-enter the application when
a user visits a page ({\sc i-csrf} 6). When the
content reaches the browser, a malicious request will be generated
towards the site that is vulnerable to {\sc csrf}.
